Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-30 bbbq_article.tex

For MHC-I, 9-mers were used, as this is the length most frequently presented in MHC-I and was used in our earlier
study (\cite{bianchi2017}). For MHC-II, 14-mers were used,  as these are the most frequently occurring
epitope length (\cite{bergseng2015different}).
We used a human (UniProt ID UP000005640\_9606), 
viral (SARS-CoV-2, UniProt ID UP000464024) 
and bacterial (\emph{Mycobacterium tuberculosis} (MTb), UniProt ID UP000001584) 
reference proteome. We used TMHMM  \richel{ref} to predict the topology 
of the proteins within these proteomes.
To predict the affinity of an epitope to a certain MHC molecule,
we used \verb;EpitopePrediction; (\cite{bianchi2017}) for MHC-I 
and \verb;MHCnuggets; \richel{ref} for MHC-II.
The 13 MHC-I haplotypes used in this study are the same as 
used in our previous study (\cite{bianchi2017}).
The most frequent MHC-II haplotypes used  were selected, with a phenotypic frequency of at least 14\% in
the human population (\cite{greenbaum2011functional}),
resulting in 21 MHC-II haplotypes.

@@

Plotting the normalized values of presented TMH-derived epitopes (where
$1.0$ denotes that the percentage of presented TMH-derived epitopes
matches the values as expected by chance) in \ref{fig:rel_presentation}
shows that MHC-II has a higher relative over-presentation of TMH-derived
epitopes, when compared to MHC-I.
The MHC-I molecule presents epitopes of shorter length than MHC-II.
We expect this to be of no influence in the presentation level
of TMH-derived epitopes, for each of the three proteomes.
We verified this, by normalizing the percentage of TMH-derived epitopes found
to the percentage of TMH-derived epitopes expected, 
where a value of $1.0$ denotes that the percentage of TMH-derived epitopes found
matches the percentage as expected by chance.
\richel{TODO: explain only the results found. Elaborate. Draw a conclusion}
Additionally, we investigated if MHC-I and MHC-II are equally prone
to present TMH-derived epitopes. 
\richel{Add exact method}
See \ref{fig:rel_presentation} and \ref{fig:rel_presentation_per_haplotype}.

>>>>

For MHC-I, 9-mers were used, as this is the length most frequently presented in MHC-I and was used in our earlier
study (\cite{bianchi2017}). For MHC-II, 14-mers were used,  as these are the most frequently occurring
epitope length (\cite{bergseng2015different}).
We used a human (UniProt ID UP000005640\_9606), 
viral (SARS-CoV-2, UniProt ID UP000464024) 
and bacterial (\emph{Mycobacterium tuberculosis} (MTb), UniProt ID UP000001584) 
reference proteome. We used TMHMM (\cite{krogh2001predicting}) to predict the topology 
of the proteins within these proteomes.
To predict the affinity of an epitope to a certain MHC molecule,
we used \verb;EpitopePrediction; (\cite{bianchi2017}) for MHC-I 
and \verb;MHCnuggets; (\cite{shao2020high}) for MHC-II.
The 13 MHC-I haplotypes used in this study are the same as 
used in our previous study (\cite{bianchi2017}).
The most frequent MHC-II haplotypes used  were selected, with a phenotypic frequency of at least 14\% in
the human population (\cite{greenbaum2011functional}),
resulting in 21 MHC-II haplotypes.

@@

Plotting the normalized values of presented TMH-derived epitopes (where
$1.0$ denotes that the percentage of presented TMH-derived epitopes
matches the values as expected by chance) in \ref{fig:rel_presentation}
shows that MHC-II has a higher relative over-presentation of TMH-derived
epitopes, when compared to MHC-I.
The MHC-I molecule presents epitopes of shorter length than MHC-II.
We expect this to be of no influence in the presentation level
of TMH-derived epitopes, for each of the three proteomes.
We verified this, by normalizing the percentage of TMH-derived epitopes found
to the percentage of TMH-derived epitopes expected, 
where a value of $1.0$ denotes that the percentage of TMH-derived epitopes found
matches the percentage as expected by chance.
\richel{explain only the results found. Elaborate. Draw a conclusion}
Additionally, we investigated if MHC-I and MHC-II are equally prone
to present TMH-derived epitopes. 
\richel{Add exact method}
See \ref{fig:rel_presentation} and \ref{fig:rel_presentation_per_haplotype}.
